First steps towards a formalization of Forcing

### 2018-06-24 LSFA/isabelle-zf.tex
macros edrel, eclose; abstract; isabelle-zf es Section

%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%
\subsection{Isabelle/ZF}

@@

% locales

>>>>

%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%-%
\section{Isabelle/ZF}

@@

Mathematical texts usually start by fixing the context which defines
both the theory, sometimes one explicitly introduces also the axioms
of the theory, and syntactical conventions. One might then either
prove that some structure satisfies the axioms and conclude some
result about the structure or extend and refine the theory
itself. \emph{Locales}~\cite{ballarin2010tutorial} are Isabelle's
facilities to define contexts; there are also operations to
\emph{extend} a locale with further assumptions (for example, moving
from lattices to distributive lattices), to \emph{interpret} locales
(roughly related to signature morphisms of universal algebra), and to
\emph{instantiate} locales on concrete structures. In our work, we
use locales to organize the formalization and to make explicit the
assumptions of the most important results.
% locales
